---
title: "Mission Data 2nd"
author: "Ward"
date: "7/30/2018"
output: html_document
---

---
title: "Grant Mission Project"
author: "Ward"
date: "7/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/Mission_use files on desktop_4_GitHUB")
library(dplyr)
library(ggplot2)
library(readr)
library(Hmisc)
library(ggthemes)
library(knitr)
library(xtable)
library(pander)
library(car)
library(tidyr)
#reading in data
report_1 <- read.csv("1.csv")
report_2 <- read.csv("2.csv")
report_3 <- read.csv("3.csv")
report_4 <- read.csv("4.csv")
report_5 <- read.csv("5.csv")
report_6 <- read.csv("6.csv")
report_7 <- read.csv("7.csv")
report_8 <- read.csv("8.csv")
report_9 <- read.csv("9.csv")
report_10 <- read.csv("10.csv")
report_11 <- read.csv("11.csv")
report_12 <- read.csv("12.csv")
report_13 <- read.csv("13.csv")
report_14 <- read.csv("14.csv")
```

#only selecting 'Company', 'First Name', and 'Last Name' columns from datasets 
```{r}
company_2 <- report_2%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_3 <- report_3%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_4 <- report_4%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_5 <- report_5%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_6 <- report_6%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_7 <- report_7%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_11 <- report_11%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_12 <- report_12%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_13 <- report_13%>%
  select(Company, First.Name, Last.Name)
```

```{r}
company_14 <- report_14%>%
  select(Company, First.Name, Last.Name)
```

#rbind all datasets that contain 'Company', 'First Name', and 'Last Name' columns into one dataset
```{r}
Company_all <- rbind(company_2, company_3, company_4, company_5, company_6, company_7, company_11, company_12, company_13, company_14)
```

```{r}
Company_all <- Company_all%>%
  rename("First_Name" = First.Name)%>%
  rename("Last_Name" = Last.Name)
```

#combining 'First Name' and 'Last Name' columns to create new 'Name' column
```{r}
Company_all <- Company_all%>%
  mutate(Name = paste(First_Name, Last_Name))
```

#deleting 'First Name' and 'Last Name' columns
```{r}
Company_all$First_Name <- NULL
Company_all$Last_Name <- NULL
```

#removes duplicates
```{r}
Company_all <- Company_all[!duplicated(Company_all$Name),]
```

#exporting Company dataset to working directory
```{r}
write.csv(Company_all, "Company_list_UPDATED.csv")
```


#Selecting 'Job Title' and 'How.did.you.hear.about.us.' columns from datasets
```{r}
report_1 <- report_1%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.us.)
```

```{r}
report_2 <- report_2%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_3 <- report_3%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_4 <- report_4%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_5 <- report_5%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_6 <- report_6%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_7 <- report_7%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_8 <- report_8%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.us.)
```

```{r}
report_9 <- report_9%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.us.)
```

```{r}
report_10 <- report_10%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.us.)
```

```{r}
report_11 <- report_11%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_12 <- report_12%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_13 <- report_13%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

```{r}
report_14 <- report_14%>%
  select(First.Name, Last.Name, Job.Title, How.did.you.hear.about.this.event.)
```

#cleaning column names 
```{r}
report_1 <- report_1%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.us.)
```

```{r}
report_2 <- report_2%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_3 <- report_3%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_4 <- report_4%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_5 <- report_5%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_6 <- report_6%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_7 <- report_7%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_8 <- report_8%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.us.)
```

```{r}
report_9 <- report_9%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.us.)
```

```{r}
report_10 <- report_10%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.us.)
```

```{r}
report_11 <- report_11%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_12 <- report_12%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_13 <- report_13%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

```{r}
report_14 <- report_14%>%
  rename("Job_Title" = Job.Title)%>%
  rename("How_did_you_hear" = How.did.you.hear.about.this.event.)
```

#rbinding report_1 through report_14 together (contains now )
```{r}
report_1_to_14 <- rbind(report_1, report_2, report_3, report_4, report_5, report_6, report_7, report_8, report_9, report_10, report_11, report_12, report_13, report_14)
```

```{r}
report_1_to_14 <- report_1_to_14%>%
  mutate(Name = paste(First.Name, Last.Name))
```

```{r}
report_1_to_14$First.Name = NULL
report_1_to_14$Last.Name = NULL
```

```{r}
report_1_to_14<- report_1_to_14[!duplicated(report_1_to_14$Name),]
```

```{r}
job_title <- report_1_to_14%>%
  select(Job_Title,Name)
```

#exporting job_title dataset to working directory
```{r}
write.csv(job_title, "job_title_UPDATED.csv")
```

```{r}
how_did_you_hear <- report_1_to_14%>%
  select(How_did_you_hear, Name)
```

#getting rid of irrelevant symbols and words from survey data
```{r}
how_did_you_hear$How_did_you_hear <- gsub("na", " ", how_did_you_hear$How_did_you_hear)
how_did_you_hear$How_did_you_hear <- gsub("yes", " ", how_did_you_hear$How_did_you_hear)
how_did_you_hear$How_did_you_hear <- gsub("no", " ", how_did_you_hear$How_did_you_hear)
how_did_you_hear$How_did_you_hear <- gsub("N/A", " ", how_did_you_hear$How_did_you_hear)
how_did_you_hear$How_did_you_hear <- gsub("Yes", " ", how_did_you_hear$How_did_you_hear)
how_did_you_hear$How_did_you_hear <- gsub("No", " ", how_did_you_hear$How_did_you_hear)
```

#filtering out unrelated rows
```{r}
how_did_you_hear <- how_did_you_hear%>%
  filter(How_did_you_hear != "")
```

```{r}
write.csv(how_did_you_hear, "how_did_you_hear_UPDATED.csv")
```









